Extracting data for time slice analyses

### 2017-12-20 analyses/01-extract-data-for-analyses.Rmd
Change dispRity version to release version

## The latest version of dispRity 
install_github("TGuillerme/dispRity")
library(dispRity) 
```

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
# matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
#                                  uncertainty.threshold = 0.95)
# saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))

>>>>

## The latest version of dispRity 
install_github("TGuillerme/dispRity@v0.5")
library(dispRity) 
```

@@

## Estimating the ancestral states (with a uncertainty threshold of 0.95)
matrix_nodes <- AncStateEstMatrix(matrix, tree, estimate.allchars = TRUE,
                                 uncertainty.threshold = 0.95)
saveRDS(matrix_nodes, file = paste0("../data/processed/ancestral_states.", slug ,".Rda"))
